Timely Object Recognition

### 2012-06-01 writeups/nips12/introduction.tex
exactly 8+1 pages

In most real-world applications of object recognition, performance is time-sensitive and inherently tied to the many-class nature of the world.
In robotics, a small finite amount of processing power per unit time is all that is available for robust object detection if the robot is to usefully interact with humans.
In large-scale detection system deployments, such as for image search, results need to be obtained quickly per image as the number of images to process is large and growing.
In these cases, an acceptable answer at a reasonable time may be more valuable than the best answer given too late.

@@

The conventional approach to evaluation of results on visual category
recognition does not consider efficiency and evaluates performance
indepednently across classes.  
We argue that the key to tackling such problems of dynamic recognition resource allocation is to start asking a new question:
\emph{What is the best performance we can get on a budget?}
We propose a new \emph{timeliness} measure of performance vs. time (shown in Figure~\ref{fig:figure1}), which evalutes the time efficiency of multi-class detection.

We present a method based on reinforcement learning that takes various detectors and classifiers as black boxes, and learns a dynamic policy for selecting detector and other actions to achieve the highest performance under this evaluation.
We are able to obtain better performance than baselines when there is less time available than is needed to run all detectors.

A hypothetical recognition system for a vision-based advertising deployment presents a motivational case study.
The system will have different accuracies for objects of different classes; detections will have different values based on confidence and class; and the queue of unprocessed images will vary in size.
The detection strategy to maximize profit in such an environment should depend on all of these variables.
We explore this scenario using the PASCAL VOC datasets and evaluation regimes, and show that our learned dynamic policy offers a better strategy than a random or optimal static ordering of detectors.

>>>>

In most real-world applications of object recognition, performance is time-sensitive and inherently tied to the many-class nature of the world.
In robotics, a small finite amount of processing power per unit time is all that is available for robust object detection if the robot is to usefully interact with humans.
In large-scale detection systems (e.g. image search), results need to be obtained quickly per image as the number of items to process is constantly growing.
In these cases, an acceptable answer at a reasonable time may be more valuable than the best answer given too late.

@@

The conventional approach to evaluation of visual category recognition does not consider efficiency and evaluates performance independently across classes.
We argue that the key to tackling problems of dynamic recognition resource allocation is to start asking a new question:
\emph{What is the best performance we can get on a budget?}

We propose a new \emph{timeliness} measure of performance vs. time (shown in Figure~\ref{fig:figure1}), and present a method based on reinforcement learning that takes various detectors and classifiers as black boxes, and learns a dynamic policy for selecting detector and other actions to achieve the highest performance under this evaluation.
We are able to obtain better performance than baselines when there is less time available than is needed to run all detectors.

A hypothetical system for vision-based advertising presents a case study.
The system will have different values and accuracies for objects of different classes, and the queue of unprocessed images will vary in size.
The detection strategy to maximize profit in such an environment has to be dynamic.
We explore this scenario using the PASCAL VOC datasets and evaluation regimes, and show that our learned dynamic policy offers a better strategy than a random or optimal static ordering of detectors.

### 2012-06-01 writeups/nips12/nips2012.tex
printed
exactly 8+1 pages

\begin{abstract}
In a large visual multi-class detection framework, the timeliness of results can be crucial.
We are motivated by situations where running all detectors would take an unacceptably long time, and the best answer must be given by some deadline.
Our method for \emph{timely multi-class detection} aims to give the best possible performance at any single point after a start time; it is terminated at a deadline time.
Toward this goal, we formulate a dynamic, \emph{closed-loop} policy guided by inference of the contents of the image in order to decide which detector to deploy next.
In contrast to previous work, our method significantly diverts from the predominant greedy strategies, and is able to learn to employ actions with deferred value.
We evaluate our method with respect to performance on a novel \emph{timeliness} measure, computed as the area under an Average Precision (AP) vs. Time
curve.
We conduct experiments on the widely used PASCAL VOC object detection dataset.
With our method, if execution is stopped when only half the detectors have been run, our method obtains $66\%$ better AP than a random ordering, and $14\%$ better performance than an intelligent baseline.
Overall, our method obtains at least $11\%$ better performance on the AP vs. Time evaluation on PASCAL VOC.
% At time of publication we will make our code available, which is easily extendible to new detectors, classifiers, tasks and reward functions due to the modular nature of our formulation.
\end{abstract}

\input{introduction.tex} % includes Evaluation section
\input{related.tex}
\input{technical.tex}
\input{evaluation.tex}

>>>>

\begin{abstract}
In a large visual multi-class detection framework, the timeliness of results can be crucial.
%We are motivated by situations where running all detectors would take an unacceptably long time, and the best answer must be given by some deadline.
Our method for \emph{timely} multi-class detection aims to give the best possible performance at any single point after a start time; it is terminated at a deadline time.
Toward this goal, we formulate a dynamic, \emph{closed-loop} policy that infers the contents of the image in order to decide which detector to deploy next.
In contrast to previous work, our method significantly diverts from the predominant greedy strategies, and is able to learn to take actions with deferred values.
We evaluate our method with a novel \emph{timeliness} measure, computed as the area under an Average Precision (AP) vs. Time curve.
Experiments are conducted on the eminent PASCAL VOC object detection dataset.
If execution is stopped when only half the detectors have been run, our method obtains $66\%$ better AP than a random ordering, and $14\%$ better performance than an intelligent baseline.
On the timeliness measure, our method obtains at least $11\%$ better performance.
Our code, to be made available upon publication, is easily extensible as it treats detectors and classifiers as black boxes and learns from execution traces using reinforcement learning.
\end{abstract}

\input{introduction.tex}
\input{related.tex}
\input{technical.tex}
\input{evaluation.tex}

### 2012-06-01 writeups/nips12/related.tex
more minor squeezing
exactly 8+1 pages

\subsection{Related Work}
The literature on object recognition is vast.
Here we briefly summarize work that sufficiently contextualizes our contribution.

\myparagraph{Single-class detection}
The best recent performance has come from detectors that use gradient-based features to represent objects as either a collection of local patches or as object-sized windows \cite{Dalal2005,Lowe2004}.
Classifiers are then used to distinguish between featurizations of a given class and all other possible contents of an image window.
%
Window proposal is often done exhaustively over the image space, as a ``sliding window''.
Using ``jump windows'' (window hypotheses voted on by local features) as region proposals is another common idea~\cite{Vedaldi2009,Vijayanarasimhan2011}.
For local feature-based approaches, a bounded search over the space of all possible windows works reasonably well~\cite{Lampert2008a}.
%
None of the best-performing systems treat window proposal and evaluation as a closed-loop system, with feedback from evaluation to proposal.
Some work has been done on this topic, mostly inspired by ideas from biological vision and attention research~\cite{Butko2009,Vogel2008,Paletta2005}.

\myparagraph{Context}
Context has a foundational role in vision.
One source of context is the scene or other non-detector cues; the most common scene-level feature is the GIST \cite{Oliva2001a} of the image.
For the commonly used PASCAL VOC dataset \cite{pascal-voc-2010}, GIST and other sources of context are quantitatively explored in~\cite{Divvala2009}.

Another source is inter-object context, shown to be useful for improving detection \cite{Torralba2004}.
A critical summary of the main approaches to using context for object and scene recognition is given in \cite{Galleguillos2010}.

\myparagraph{Multi-Class Detection}
Work on inherently multi-class detection focuses largely on making detection time sublinear in the number of classes through sharing features \cite{Torralba2007,Fan2005,Razavi2011}.
A proposed post-processing extension to detection systems uses structured prediction to incorporate multi-class context as a principled replacement for the common post-processing step of non-maximum suppression \cite{Desai2009}.

>>>>

%\subsection{Related Work}
The literature on object recognition is vast.
Here we briefly summarize work that sufficiently contextualizes our contribution:

\myparagraph{Single-class detection}
The best recent performance has come from detectors that use gradient-based features to represent objects as either a collection of local patches or as object-sized windows \cite{Dalal2005,Lowe2004}.
Classifiers are then used to distinguish between featurizations of a given class and all other possible contents of an image window.
%
Window proposal is often done exhaustively over the image space, as a ``sliding window''.
Using ``jump windows'' (window hypotheses voted on by local features) as region proposals is another common idea~\cite{Vedaldi2009,Vijayanarasimhan2011}.
For local feature-based approaches, a bounded search over the space of all possible windows works reasonably well~\cite{Lampert2008a}.
%
None of the best-performing systems treat window proposal and evaluation as a closed-loop system, with feedback from evaluation to proposal.
Some work has been done on this topic, mostly inspired by ideas from biological vision and attention research~\cite{Butko2009,Vogel2008}.

\myparagraph{Context}
Context has a foundational role in vision.
One source of context is the scene or other non-detector cues; the most common scene-level feature is the GIST \cite{Oliva2001a} of the image.
For the commonly used PASCAL VOC dataset \cite{pascal-voc-2010}, GIST and other sources of context are quantitatively explored in~\cite{Divvala2009}. 
%
Another source is inter-object context, shown to be useful for improving detection \cite{Torralba2004}.
A critical summary of the main approaches to using context for object and scene recognition is given in \cite{Galleguillos2010}.

\myparagraph{Multi-Class Detection}
Work on inherently multi-class detection focuses largely on making detection time sublinear in the number of classes through sharing features \cite{Torralba2007,Fan2005}.
A proposed post-processing extension to detection systems uses structured prediction to incorporate multi-class context as a principled replacement for the common post-processing step of non-maximum suppression \cite{Desai2009}.
